### 2016-08-24 analysis-note-v2/RTPC.tex
add the pi0 production yield for both DVCS channels in section 4.5.1

In the left module of the RTPC, figure \ref{fig:dedx_p_exp_2nd}, one notices an 
additional unexpected lower peak (dEdx$_{exp}$/dEdx$_{sim} \sim$ 0.3). These 
events pass all the elastic requirements but for some reasons they have lower 
ADC values. They represent around $7\%$ of all the elastic events. After 
extended studies, the nature of these particles is not identified yet. We note 
that this is a global phenomenon in the left module as 94$\%$ of the left 
module's pads are involved in both some low and high dEdx events. For instance, 
figure \ref{fig:Chann_706} shows the average ADC versus TDC distributions for 
the recorded hits in one of these pads in the left module. For the calibration 
procedures, the events with low dEdx were excluded as we do not fully 
understand their nature, see figure \ref{fig:dedx_cal_left}.\\
\begin{figure}[tbp]
\centering
\includegraphics[scale=0.4]{fig_rtpc/Chan_706_1.png}
\includegraphics[scale=0.4]{fig_rtpc/Chan_706_2.png}
\caption{The average ADC vs. TDC distributions of the experimental hits 
   recorded for the elastic events in one pad of the left module, pad number 
   706.  On the top: the distribution for the elastic tracks in the region 
   where dEdx$_{exp}$/dEdx$_{sim} $ $\sim$ 1. On the bottom: the distribution 
for the elastic tracks that exhibit dEdx$_{exp}$/dEdx$_{sim} $ $\sim$ 0.3.}
\label{fig:Chann_706}
\end{figure}

@@

\begin{figure}[tbp]
%\hspace{-0.4in}
\includegraphics[scale=0.3]{fig_rtpc/noisy_pad_before_rejection.png}
\includegraphics[scale=0.3]{fig_rtpc/noisy_pad_after_rejection.png}
%\vspace{-0.3in}
\caption{The integrated ADC vs. TDC of the hits for good tracks before (left) 
and after (right) the oscillatory noise reduction, for a particular pad with 
strong noise. The color scale on the z-axis is for the hit yield and identical 
in both plots as well as the event sample.}
\label{fig:Adcvstdcnoise}
\end{figure}

@@

\begin{figure}[htbp]\centering
  \includegraphics[width=12cm]{fig_rtpc/Occ2d_norej2.png}
  \includegraphics[width=12cm,trim={2.5cm 0 0 0},clip]{fig_rtpc/Occ2d_rej.png}
  \caption{Occupancies before (top) and after (bottom) the two noise reduction algorithms.  The event sample and occupancy color scales are identical in the two plots.\label{fig:occ_noiserej}}
\end{figure}

>>>>

In the left module of the RTPC, on the bottom panel of figure \ref{fig:dedxre}, 
one notices an additional unexpected lower peak (dEdx$_{exp}$/dEdx$_{sim} \sim$ 
0.3). These events pass all the elastic requirements but for some reasons they 
have lower ADC values. They represent around $7\%$ of all the elastic events.  
After extended studies, the nature of these particles is not identified yet. We 
note that this is a global phenomenon in the left module as 94$\%$ of the left 
module's pads are involved in both some low and high dEdx events. For instance, 
figure \ref{fig:Chann_706} shows the average ADC versus TDC distributions for 
the recorded hits in one of these pads in the left module. For the calibration 
procedures, the events with low dEdx were excluded as we do not fully 
understand their nature, see figure \ref{fig:dedx_cal_left}.\\
\begin{figure}[tbp]
\centering
\includegraphics[scale=0.4]{fig_rtpc/Chan_706_1.png}
\includegraphics[scale=0.4]{fig_rtpc/Chan_706_2.png}
\caption{The average ADC vs. TDC distributions of the experimental hits 
   recorded for the elastic events in one pad of the left module, pad number 
   706.  On the top: the distribution for the elastic tracks in the region 
   where dEdx$_{exp}$/dEdx$_{sim} $ $\sim$ 1. On the bottom: the distribution 
for the elastic tracks that exhibit dEdx$_{exp}$/dEdx$_{sim} $ $\sim$ 0.3.}
\label{fig:Chann_706}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[scale=0.3]{fig_rtpc/noisy_pad_before_rejection.png}
\includegraphics[scale=0.3]{fig_rtpc/noisy_pad_after_rejection.png}
\caption{The integrated ADC vs. TDC of the hits for good tracks before (left) 
and after (right) the oscillatory noise reduction, for a particular pad with 
strong noise. The color scale on the z-axis is for the hit yield and identical 
in both plots as well as the event sample.}
\label{fig:Adcvstdcnoise}
\end{figure}

@@

\begin{figure}[htbp]\centering
  \includegraphics[width=12.3cm]{fig_rtpc/Occ2d_norej2.png}
  \includegraphics[width=12cm,trim={1.9cm 0 0 0},clip]{fig_rtpc/Occ2d_rej.png}
  \caption{Occupancies before (top) and after (bottom) the two noise reduction algorithms.  The event sample and occupancy color scales are identical in the two plots.\label{fig:occ_noiserej}}
\end{figure}

### 2016-08-24 analysis-note-v2/analysis-2.tex
add the pi0 production yield for both DVCS channels in section 4.5.1

\begin{figure}[tp]
\centering
\includegraphics[scale=0.30]{fig_dvcs/e4Hegamma_e4Hepi0_Q2.png}
\includegraphics[scale=0.30]{fig_dvcs/e4Hegamma_e4Hepi0_xB.png}
\includegraphics[scale=0.30]{fig_dvcs/e4Hegamma_e4Hepi0_t.png}
\includegraphics[scale=0.30]{fig_dvcs/e4Hegamma_e4Hepi0_Phi.png}
\caption{The coherent channel acceptance ratios as a function of the kinematic 
variables: $Q^{2}$ (top left), $x_{B}$ (top right), $-t$ (bottom left), and 
$\phi$ (bottom right). }
\label{fig:coh_acceptance _ratios}
\end{figure}

\begin{figure}[tp]
\centering
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_Q2.png}
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_xB.png}
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_t.png}
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_Phi.png}
\caption{The incoherent channel acceptance ratios as a function of the 
kinematic variables: $Q^{2}$ (top left), $x_{B}$ (top right), $-t$ (bottom 
left), and $\phi$ (bottom right).}
\label{fig:incoh_acceptance _ratios}
\end{figure}

>>>>

Figure \ref{fig:cont_yield} presents the measured coherent and incoherent 
$\pi^{0}$ production yield with respect to the measured DVCS events. On both 
channels, the yield increases strongly with -$t$, with a mean of 9$\%$ (34$\%$) 
for the coherent (incoherent) channel. Multiplying the $\pi^{0}$ production 
yield with the mean coherent (incoherent) acceptance ratio yields to an 
estimation of the coherent (incoherent) background yield to be about 3$\%$ 
(7$\%$).\\

\begin{figure}[tpb]
\centering
\includegraphics[scale=0.30]{fig_dvcs/e4Hegamma_e4Hepi0_Q2.png}
\includegraphics[scale=0.30]{fig_dvcs/e4Hegamma_e4Hepi0_xB.png}
\includegraphics[scale=0.30]{fig_dvcs/e4Hegamma_e4Hepi0_t.png}
\includegraphics[scale=0.30]{fig_dvcs/e4Hegamma_e4Hepi0_Phi.png}
\caption{The coherent channel acceptance ratios as a function of the kinematic 
variables: $Q^{2}$ (top left), $x_{B}$ (top right), $-t$ (bottom left), and 
$\phi$ (bottom right). }
\label{fig:coh_acceptance _ratios}
\end{figure}

\begin{figure}[tpb]
\centering
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_Q2.png}
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_xB.png}
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_t.png}
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_Phi.png}
\caption{The incoherent channel acceptance ratios as a function of the 
kinematic variables: $Q^{2}$ (top left), $x_{B}$ (top right), $-t$ (bottom 
left), and $\phi$ (bottom right).}
\label{fig:incoh_acceptance _ratios}
\end{figure}

\begin{figure}[tpb]
\includegraphics[scale=0.37]{fig_updated/T_ratio_pi0_dvcs_Coh_t.png}
\includegraphics[scale=0.37]{fig_updated/T_ratio_pi0_dvcs_InCoh_t.png}
\caption{The experimental coherent (left) and incoherent (right) $\pi^{0}$ 
yield with respect to the experimental DVCS events as a function of the 
transfered momentum squared -$t$. The data is integrated over the kinematical 
variables $Q^2$, $x_B$, and $\phi$.  }
\label{fig:cont_yield}
\end{figure}

### 2016-08-24 analysis-note-v2/results.tex
add the pi0 production yield for both DVCS channels in section 4.5.1

\begin{figure}[tpb]
\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_Q2_90.pdf} 
\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_xB_90.pdf}
\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_t_90.pdf} 
\caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) of 
   the incoherent $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). Middle 
   panel: the red and the blue curves are theoretical calculations from 
   \cite{simonetta_2}. On the bottom: the green circles are the HERMES 
$-A_{LU}$ (positron beam was used) inclusive measurements \cite{HERMES_BSA}, 
the colored curves represent theoretical calculations from \cite{simonetta_2}.  
} \label{fig:incoh_Q2_xB_t_ALU}
\end{figure}

>>>>

\begin{figure}[tpb]
   \centering
\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_Q2_90.pdf}\\ 
\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_xB_90.pdf}\\
\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_t_90.pdf} \\ 
\caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) of 
   the incoherent $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). Middle 
   panel: the red and the blue curves are theoretical calculations from 
   \cite{simonetta_2}. On the bottom: the green circles are the HERMES 
$-A_{LU}$ (positron beam was used) inclusive measurements \cite{HERMES_BSA}, 
the colored curves represent theoretical calculations from \cite{simonetta_2}.  
} \label{fig:incoh_Q2_xB_t_ALU}
\end{figure}
